\mytitle

### 2021-12-19 paper.tex
formulation
improve formulation

The third fastest implementation is provided by Cephes, which is by a
factor two slower than the implementation in the appendix.  This
longer runtime has several reasons: For one, Cephes uses a rational
function approximation with more terms in the numerator and
denominator.  Furthermore, Cephes evaluates the numerator and
denominator polynomials using Horner's scheme, which is purely
sequential.\footnote{For $x>1$ Cephes calculates $\ln(x)$ twice, which
  leads to a further increased runtime when a different interval for
  $x$ is chosen.}

>>>>

The third fastest implementation is provided by Cephes, which is by a
factor two slower than the implementation prestend in this paper.
This longer runtime has several reasons: For one, Cephes uses a
rational function approximation with more terms in the numerator and
denominator.  Furthermore, Cephes evaluates the numerator and
denominator polynomials using Horner's scheme, which is purely
sequential.\footnote{For $x>1$ Cephes calculates $\ln(x)$ twice, which
  leads to a further increased runtime when a benchmark interval with
  $x>1$ is chosen.}
